Regular singular Volterra equations on complex domains

### 2023-08-01 reg-sing-volterra.tex
Fix the comments in orange

\textcolor{RoyalBlue}{$f_0 \in F\zeta^{\tau-1} + O(\zeta^\tau)$ near $\zeta = 0$ for some non-zero constant $F$.}
\end{rmk}
\begin{thm}\label{thm:proto-growth}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}} and {\em \eqref{cond:slow}} from Section~\ref{setting:basic}. Then the solution $f_0$ from {\em Theorem~\ref{thm:basic_volterra}} is uniformly of exponential type $\lambda_0$ \textcolor{orange}{[explain what we mean by ``uniformly''---for example, by mentioning the discussion in Section~\ref{sec:fn-space-defs}, including the footnote]}. In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}

@@

\begin{thm}\label{thm:general_volterra}
    Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}. Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section \ref{setting:perturbed}. Then the Volterra equation 
    \[f = \left[ \hardpart + \softpart \right] f\]
    admits a unique solution in the affine subspace
\[ f_0 + \singexp{\tau-1+\epsilon}{{\Lambda}}(\Omega) \]
of the function space $\singexp{\tau-1}{{\Lambda}}(\Omega)$, defined in Section~\ref{fn-spaces}, for $\Lambda$ ``big enough'' (meaning $\Lambda>\lambda_\Delta$, and we may require $\Lambda \gg \lambda_\Delta$). The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
\end{thm}

@@

Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\Omega$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$. One might describe these functions as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $. We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} They form a space $\singexp{0}{\Lambda}(\Omega)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\Omega e^{-\Lambda|\zeta|}\,|f|$. With respect to the seminorm on $\holo(\Omega)$ given by a compact set $K \subset \Omega$, the inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ has norm $\sup_K e^{\Lambda |\zeta|}$. That means the inclusion is continuous.
\begin{prop}\label{exp-complete}
The space $\singexp{0}{\Lambda}(\Omega)$ is complete.
\end{prop}
\begin{proof}
Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{0}{\Lambda}(\Omega)$. The inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$ given by $|f| \mapsto \sup_K |f|$ for compact subsets $K \subset \Omega$, so our sequence is Cauchy in $\holo(\Omega)$ too. Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\Omega)$ will always converge in the topology of $\holo(\Omega)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.

@@

\textcolor{orange}{[edit to emphasize instead that we can make $\sigma - \tau$ arbitrarily small]} 
The constant $\sigma:=\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} > \tau $, and by choosing $\delta$ small enough we can make $\sigma-\tau$ arbitrary small. We will use this fact in Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.

@@

\begin{rmk}
    Proposition \ref{prop:construction} and Proposition \ref{prop:asymptotic at zero} together prove Theorem \ref{thm:basic_volterra}. 
\end{rmk}

@@

Going back to the end of Section~\ref{first-steps}, suppose that $a \in \far$. We know from Conditions \eqref{cond:diag-basic} and \eqref{cond:eps-lambda} that \textcolor{orange}{[by nudging the exponent a little bigger than $\lambda_\Delta$---change this in what follows]} we can find a constant $M$ for which

@@

\begin{proof}

@@

By Theorem \ref{thm:basic_volterra} and \ref{thm:proto-growth} (proved in Section \ref{sec:construction}), there exists a function $f_0\in \singexp{\tau-1}{\lambda_0}(\Omega)$ such that $\hardpart f_0= f_0$, hence we make the following \textit{ansatz}

@@

with $f_\star\in\singexp{\tau-1+\epsilon}{\lambda}(\Omega)$. Plugging-it in equation $\varphi= \volterra \varphi$ we get

@@

Therefore, solving the equation $ f = \volterra f$ is equivalent to finding a fixed point $f_\star$ of the affine-linear map

@@

Equations of the form \eqref{eqn:level 1 ode} were called {\em level $1$} by Ecalle (see \cite[Section 2.1]{EcalleIII}). For instance, the modified Bessel equation is of level $1$, and we study its solutions explicitly in {\tt borel-regularity}.

>>>>

\textcolor{RoyalBlue}{$f_0 \in F\zeta^{\tau-1} + O(\zeta^\tau)$ near $\zeta = 0$ for some non-zero constant $F$.}
\end{rmk}
\begin{thm}\label{thm:proto-growth}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}} and {\em \eqref{cond:slow}} from Section~\ref{setting:basic}. Then the solution $f_0$ from {\em Theorem~\ref{thm:basic_volterra}} is uniformly of exponential type $\lambda_0$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $. We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}

@@

\begin{thm}\label{thm:general_volterra}
    Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}. Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section \ref{setting:perturbed}. Then the Volterra equation 
    \[f = \left[ \hardpart + \softpart \right] f\]
    admits a unique solution in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$, defined in Section~\ref{fn-spaces}. The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
\end{thm}

@@

Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\Omega$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$. One might describe these functions as being uniformly of exponential type $\Lambda$. They form a space $\singexp{0}{\Lambda}(\Omega)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\Omega e^{-\Lambda|\zeta|}\,|f|$. With respect to the seminorm on $\holo(\Omega)$ given by a compact set $K \subset \Omega$, the inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ has norm $\sup_K e^{\Lambda |\zeta|}$. That means the inclusion is continuous.
\begin{prop}\label{exp-complete}
The space $\singexp{0}{\Lambda}(\Omega)$ is complete.
\end{prop}
\begin{proof}
Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{0}{\Lambda}(\Omega)$. The inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$ given by $|f| \mapsto \sup_K |f|$ for compact subsets $K \subset \Omega$, so our sequence is Cauchy in $\holo(\Omega)$ too. Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\Omega)$ will always converge in the topology of $\holo(\Omega)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.

@@

The constant $\sigma:=\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} > \tau $, and by choosing $\delta$ small enough we can make $\sigma-\tau$ arbitrary small. We will use this fact in Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.

@@

\begin{rmk}
   {\em Proposition \ref{prop:construction}} and {\em Proposition \ref{prop:asymptotic at zero}} together prove {\em Theorem \ref{thm:basic_volterra}}. 
\end{rmk}

@@

Going back to the end of Section~\ref{first-steps}, suppose that $a \in \far$. We know from Conditions \eqref{cond:diag-basic} and \eqref{cond:eps-lambda} that we can find a constant $M$ for which

@@

\begin{proof}[Proof of Theorem~\ref{thm:general_volterra}]

@@

By Theorem \ref{thm:basic_volterra} and \ref{thm:proto-growth} (proved in Section \ref{sec:construction}), there exists a function $f_0\in \singexp{\tau-1}{\lambda_0}(\Omega)$ such that $\hardpart f_0= f_0$. Hence we can solve the Volterra equation

\begin{equation}\label{eqn:volterra}
    f = \volterra f
\end{equation}

by the following \textit{ansatz}

@@

with $f_\star\in\singexpalg{\tau-1+\epsilon}(\Omega)$. Plugging-it in equation \eqref{eqn:volterra} we get

@@

Therefore, solving the equation \eqref{eqn:volterra} is equivalent to finding a fixed point $f_\star$ of the affine-linear map

@@

Equations of the form \eqref{eqn:level 1 ode} are called {\em level $1$} by Ecalle (see \cite[Section 2.1]{EcalleIII}). For instance, the modified Bessel equation is of level $1$, and we'll study its solutions explicitly in \cite{borel_reg}.
